---
title: 'Class 6b: Data analysis of scalar implicature E5'
author: "Mike Frank"
date: "February 11, 2016"
output: 
  html_document:
    toc: true
---
# !diagnostics off
```{r}
rm(list=ls())
library(tidyverse)
library(jsonlite)
# library(quickpsy)
# library(boot)
library(lsr)
library(ez)

library(psyphy)
```

# Data prep

```{r}
path <- "~/class/StanfordPsych254/stormer/"
files <- dir(paste0(path,"mturk/sandbox-results/"), 
             pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste0(path, "mturk/sandbox-results/",f)
  # jd <- fromJSON(paste(readLines(jf), collapse=""))
  jd <- jsonlite::fromJSON(paste(readLines(jf)), flatten=TRUE)
  stimCond <- jd$answers$data$stimCond
  resp <- jd$answers$data$data
  id <- data.frame(workerid = jd$WorkerId)
  id <- cbind(id,stimCond,resp)

  d.raw <- bind_rows(d.raw, id)
}

# Number of participants
length(unique(d.raw$workerid))
```
stringasfactors
Data cleanup

```{r}
d.raw[sapply(d.raw, is.character)] <- lapply(d.raw[sapply(d.raw, is.character)], as.factor)
d.raw$face <- factor(d.raw$face)
d.raw$testContrast <- factor(d.raw$testContrast)

head(d.raw)

d<-d.raw %>%
  mutate(testVertical = factor(ifelse((testPos=="left"&leftUp==T)|(testPos=="right"&leftUp==F),"up",
                               ifelse((testPos=="left"&leftUp==F)|(testPos=="right"&leftUp==T),"down",NA)))) %>%
  mutate(chosen = factor(ifelse(testVertical==keypress,"test","standard")))

 # d2<-d.raw %>%
 #  mutate(testVertical = ifelse((testPos=="left"&leftUp==T)|(testPos=="right"&leftUp==F),"up", "down"))
 # d2 <- d2%>%
 #   mutate(chosen = ifelse(testVertical==keypress,"test","standard"))
```

# More sanity checks

Start with a histogram, *ALWAYS*. 
```{r}
d %>% ggplot(aes(x=rt)) +
  geom_histogram() +
  ggthemes::theme_few()

d %>% ggplot(aes(x=keypress)) +
  geom_bar() +
  ggthemes::theme_few()

d %>% ggplot(aes(x=chosen)) +
  geom_bar() +
  ggthemes::theme_few()

d %>% ggplot(aes(x=testVertical,fill=chosen)) +
  geom_bar(position = "dodge") +
  facet_wrap(~workerid) +
  ggthemes::theme_few()
```

```{r}
tbl <- d %>% 
  group_by(workerid,cue,testContrast) %>%
  summarise(n=n(),testChosen=sum(chosen=="test"), 
            standardChosen=sum(chosen=="standard"),pctTest=testChosen/n*100) 

tbl <- tbl %>%
  group_by(workerid) %>%
  mutate(workerMean=mean(pctTest))

t <- t %>%
  group_by(workerid) %>%
  mutate(workerMean=mean(pctTest)) %>%
  ungroup() %>%
  mutate(grandMean=mean(workerMean)) %>%
# To calculate within subject errors
# new value = old value – subject average + grand average
  mutate(newPct=pctTest-workerMean+grandMean)


print(tbl)
print(t)
```

Break down by IVs.

```{r}
d %>% ggplot(aes(x=chosen)) +
  geom_bar(position="dodge") +
  facet_grid(.~cue) +
  ggthemes::theme_few()

d %>% ggplot(aes(x=cue,fill=chosen)) +
  geom_bar(position = "dodge") +
  facet_wrap(~workerid) +
  ggthemes::theme_few()

d %>% ggplot(aes(x=cue,fill=chosen)) +
  geom_bar(position = "dodge") +
  facet_wrap(~face) +
  ggthemes::theme_few()

```
``` {r}
# prepare df for t-test & examine individual differences
d_test <- d[d$testContrast=="3",] %>% 
  group_by(workerid,cue) %>%
  summarise(n=n(),testChosen=sum(chosen=="test"), 
            pctTest=testChosen/n*100)
print(d_test)
d_test %>%
  ggplot(aes(x=cue,y=pctTest,group=workerid, color=workerid)) +
  geom_line() +
  geom_point(size=2)
  # geom_pointrange(aes(ymin=pctTest-0, ymax=pctTest+0))
  
```
pweibull(q, shape, scale = 1, lower.tail = TRUE, log.p = FALSE)
pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
``` {r} 
# plot psychometric - test face contrast * %test face chosen * cue -> facet by worker
tbl %>% ggplot(aes(x=testContrast, y=pctTest, group=cue, color=cue)) +
  geom_line(size=0) +
  geom_point(size=2.5) +
  facet_wrap(~workerid)

t<-bind_rows(tbl,tbl)
t$workerid = as.character(t$workerid)
t$workerid[11:20] = "aaa"
t$workerid = as.factor(t$workerid)
t$pctTest[11:20] = c(5,20,60,80,95,30,45,77.5,87.5,100)
t$testChosen[11:20] = t$pctTest[11:20]/100*40

# get mean psychometric
psychometric <- t %>% 
  group_by(cue,testContrast) %>%
  # mean and within subject errors
  summarise(avePct=mean(pctTest), se=sd(newPct)/sqrt(n()),
            ntrial=mean(n),aveTestChosen=mean(testChosen),
            sumTest=sum(testChosen),sumN=sum(n))
psychometric <- psychometric %>%
  mutate(RMScontrast = c(.30,.35,.39,.44,.50))
print(psychometric)
psychometric %>%
  ggplot(aes(x=RMScontrast,y=avePct,group=cue,color=cue)) +
  geom_pointrange(aes(ymin=avePct-se, ymax=avePct+se))

```
# fit psychometric functions using MLE
```{r}

# library('ggplot2')
# n <- 100
# x <- c(.2, .4, .6, .8, 1) #luminance
RMScontrast = c(.30,.35,.39,.44,.50)
x<-RMScontrast
n<-psychometric$sumN #n trial per condition
k <- psychometric$sumTest # number of times that the observer reports that can see the stimulus
y <- k/n
cue <- psychometric$cue
dat <- data.frame(cue,x, k,n, y)



# m<-2 # 2-alternative forced choice

fitting <- function(df){
  nll <- function(p) { 
  # phi <- 1/m + (1-1/m) * pweibull(df$x, p[1], p[2]) 
  phi <- pweibull(df$x, p[1], p[2]) 
  -sum(df$k * log(phi) + (df$n - df$k) * log(1 - phi))
  }
  
para <- optim(c(.7,.7), nll)$par
# para
xseq <- seq(.3,.5,.001)
yseq <- pweibull(xseq, para[1], para[2])
# yseq <- 1/m + (1-1/m) * pweibull(xseq, para[1], para[2])
# curve <- data.frame(xseq,yseq)
data.frame(xseq,yseq) #return
}

curves <- plyr::ddply(dat, ~cue, fitting)
# p<- p+ geom_line(data=curves,aes(x=xseq,y=yseq,color=cue))
# p

p<- psychometric %>%
  ggplot(aes(x=RMScontrast,y=avePct,group=cue,color=cue)) +
  geom_pointrange(aes(ymin=avePct-se, ymax=avePct+se)) +
  geom_line(data=curves,aes(x=xseq,y=yseq*100,color=cue)) +
  geom_segment(aes(x=.39,xend=.39, y=-Inf, yend=5),color="black",size=1.4) +
  ggthemes::theme_few()+ 
  xlab("Contrast Level of Test Face (RMSE)") +
  ylab("Test Face Chosen (%)") +
  theme(legend.position = c(0,1), legend.justification = c(0,1),
        legend.background= element_rect(fill=NA, color=NA),
        legend.title = element_blank()) +
  scale_color_discrete(labels=c("Standard Face Cued","Test Face Cued"),
                       guide=guide_legend(reverse=TRUE))
p

# fit<-quickpsy(dat,x,k,n,grouping=.(cue),lapses=TRUE,guess=TRUE,fun=weibull_fun,bootstrap = "none")

```
```{r}
# fit with glm

ddd<-data.frame(RMScontrast,dat$k[1:5],80-dat$k[1:5],dat$y[1:5])
colnames(ddd)<-c("RMScontrast","k","i","y")
p1<-ggplot()+
  geom_point(data=ddd,aes(x=x,y=y,color=cue))
p1
model <- glm(cbind(ddd$k,ddd$i) ~ RMScontrast, family=binomial(link=cloglog))

yseq <- predict(model,data.frame(RMScontrast=xseq),type = "response")
cur <- data.frame(xseq,yseq)
p1 <- p1 + geom_line(data = cur, aes(x = xseq, y = yseq))
p1

glmFit <- function(df) {
  model <- glm(cbind(df$k,df$i) ~ RMScontrast, family=binomial(link=cloglog))
  
  
}


n<-c(100,100,100,100,100)
k<-c(38,44,57,63,72)
i <-100-k
ddd<-data.frame(RMScontrast,k,i,n,y)

p1<-ggplot()+
  geom_point(data=ddd,aes(x=RMScontrast,y=y))
p1
model <- glm(cbind(ddd$k,ddd$i) ~ RMScontrast, family=binomial(link=logit))

yseq <- predict(model,data.frame(RMScontrast=xseq),type = "response")
cur <- data.frame(xseq,yseq)
p1 <- p1 + geom_line(data = cur, aes(x = xseq, y = yseq))
p1

```

```{r}
d$rms <-d$testContrast
levels(d$rms) <- RMScontrast
d$rms <- as.numeric(as.character(d$rms))

d$choice <- as.numeric(d$chosen) - 1

d %>% ggplot(aes(x=rms,y=choice,color=cue)) +
  geom_point(shape=21, fill=NA,alpha=0.7, 
             position=position_jitter(width =.006,height = .04)) +
  ggthemes::theme_few()

logreg <- glm(formula = choice ~ cue * rms -1, family = "binomial",d)

y_t <- predict(logreg,data.frame(cue="test",rms=xseq),type = "response")
y_s <- predict(logreg,data.frame(cue="standard",rms=xseq),type = "response")
yset <- data.frame(rbind(matrix(y_s),matrix(y_t)))
colnames(yset) = "yseq"
yset$cue <-rbind(matrix(rep("standard",npoints)), matrix(rep("test",npoints)))
yset$xseq = xseq

d %>%ggplot( aes(x=rms,y=choice)) +
  geom_point(aes(x=rms, y=choice, color=cue),shape=21, fill=NA,alpha=0.7, 
             position=position_jitter(width =.006,height = .04)) +
  geom_line(data=yset,aes(x=xseq,y=yseq,color=cue)) +
  ggthemes::theme_few() +
  geom_point(data=tbl,aes(x=rms, y=pctTest/100, color=cue))



# 
#   xlab("Contrast Level of Test Face (RMSE)") +
#   ylab("Test Face Chosen (%)") +
#   theme(legend.position = c(0,1), legend.justification = c(0,1),
#         legend.background= element_rect(fill=NA, color=NA),
#         legend.title = element_blank()) +
#   scale_color_discrete(labels=c("Standard Face Cued","Test Face Cued"),
#                        guide=guide_legend(reverse=TRUE))
```




```{r}
# test the effect of contrast level on contrast judgments
aov<-aov(pctTest ~ testContrast + Error(workerid/testContrast),data = t)
summary(aov)
aov_etasq<-etaSquared(aov)

m1<- ezANOVA(data=t, dv=pctTest, wid=workerid,within=testContrast,within_full=cue,detailed=TRUE)
m1
# library(ez)
# 
# m1 <- ezANOVA(data = data.ex4, dv = Recall, wid = Subject, within = .(Task,Valence), type = 3, detailed = TRUE)
# m1$ANOVA
```

```{r}
# conduct a paired t-test (test VS standard face, Contrast=3)
d_test
ttest<-t.test(pctTest ~ cue, d_t, paired=TRUE)
cohensD(pctTest ~ cue, data=d_t, method="paired")

d_t <- t[t$testContrast=="3",]


# tt <- t %>%
#   group_by(workerid,testContrast) %>%
#   summarise(avePct=mean(pctTest))
# m2<- ezANOVA(data=tt, dv=avePct, wid=workerid,within=testContrast,detailed=TRUE)


```

# Try using just ggplot to do our whole data analysis

```{r}
ggplot(d, aes(x = stars, y = judgment, col = degree)) + 
  geom_jitter() + 
  geom_smooth(method="lm", formula =  y ~ x + I(x^2)) +
  facet_wrap(~scale)
```

# Main Analysis (take 1)

Aggregation step. 

```{r}
ms <- d %>%
  group_by(scale, degree, stars) %>%
  summarise(mean = mean(judgment), 
            sem = sd(judgment) / sqrt(n()), 
            ci95 = 1.96*sem)
```

plotting

```{r}
ggplot(ms, aes(x = stars, y = mean, col = degree)) + 
  geom_line() + 
  geom_pointrange(aes(ymin = mean - ci95, 
                      ymax = mean + ci95)) + 
  facet_wrap(~scale)
```


# Main Analysis (take 2)

```{r}
ms <- d %>%
  group_by(scale, degree, stars) %>%
  multi_boot_standard(column = "judgment")
```

Plotting step. 

```{r}
ggplot(ms, aes(x = stars, y = mean, col = degree)) + 
  geom_line() + 
  geom_pointrange(aes(ymin = ci_lower, 
                      ymax = ci_upper)) + 
  facet_wrap(~ scale)
```

